---
output: 
    github_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

source("R/pkgs_sysreqs.R")
```


# mdsrocker

[![Docker Image CI](https://github.com/meterds/mdsrocker/actions/workflows/docker-image.yml/badge.svg)](https://github.com/meterds/mdsrocker/actions/workflows/docker-image.yml)

The Docker image `mdsgeospatial` adds a set of geospatial packages to the 
[r-ver](https://hub.docker.com/r/rocker/r-ver) base R image and is designed 
towards pipelines of spatial packages at METER Data Science. The image can be 
pulled from [Dockerhub](https://hub.docker.com/r/meterds/mdsgeospatial).

Currently, the following packages are included:

```{r, echo = FALSE}
data.table::data.table(
    Package = pkg_spatial
    , Title = sapply(pkg_spatial, \(i) packageDescription(i)$Title)
) |>
    kableExtra::kable()
```


Additionally, the following packages (for *CI/CD*) are installed: 

```{r, echo = FALSE}
data.table::data.table(
    Package = pkg_cicd
    , Title = sapply(pkg_cicd, \(i) packageDescription(i)$Title)
) |>
    kableExtra::kable()
```


## Version-stable METER Rocker images for R

Images built from this repository are: 

- r-aws-minimal: Adds only some system libraries
- r-aws-spatial: Adds only some system libraries
- r-cicd-minimal: Adds some development related packages
- r-cicd-spatial: Adds a set of spatial libraries

This image stack is based on 
[`rocker/r-ver`](https://hub.docker.com/r/rocker/r-ver)
