---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

# libraries
library(tibble)
library(dplyr)
library(purrr)
devtools::load_all(".")

# dockerhub account
account = desc::desc_get_field("Config/Dockerhub/Account")
```

# mdsrocker

<!-- badges: start -->
```{r badge, results='asis', echo=FALSE}
badge_name = "Docker Image CI"
src = glue::glue("https://github.com/{account}/mdsrocker/actions/workflows/publish-docker-images.yml/badge.svg")
href = glue::glue("https://github.com/{account}/mdsrocker/actions/workflows/publish-docker-images.yml")
glue("[![{badge_name}]({src})]({href})")
```
<!-- badges: end -->

The goal of *mdsrocker* is to provide a framework for building a stack of 
version-stable docker images based on 
[rocker/r-ver](https://hub.docker.com/r/rocker/r-ver), an *ubuntu*-based
docker image containing version-stable *base R* & a set of src build tools.

We follow the *version tag* approach of the *rocker*-project, using the image 
tag for specifying which version of R is desired 
(e.g. ``r paste("rocker/r-ver:", as.character(getRversion()))``).
Omit the tag or specify `:latest` to always receive the latest versions.

## Image stack

```{r stack, echo = FALSE}

stack = mdsrocker_dockerfiles |> 
  dplyr::select(image, description)

stack = stack |> 
  dplyr::mutate(
    image = kableExtra::cell_spec(
      image, 
      "html",
      link = glue::glue("https://hub.docker.com/r/{account}/{image}")
    )
  )

kableExtra::kable(stack, escape = FALSE)
```

## Architecture

This building system is designed as an R package. 

### Data

All relevant information is stored in *two* `data.frames` (as package data):

- `mdsrocker_installation`: *three* different software bundles for the various
  scopes of the docker images, each containing predefined sets of software 
  packages (system libraries, extra software packages, Python packages, 
  R packages) to install.

```{r installation, echo = FALSE}
kableExtra::kable(mdsrocker_installation)
```

- `mdsrocker_dockerfiles`: *four* dockerfile specifications, each containing 
  the relevant information for generating the dockerfiles.

```{r dockerfiles, echo = FALSE}
mdsrocker_dockerfiles |> 
  dplyr::select(-description) |> 
  kableExtra::kable()
```

### Scripts & Files

In this building system, 

- standalone shell scripts containing all the install logic are located under 
  the `scripts/` directory, 
- dockerfiles used in the Github Actions workflow to build the images are 
  located under `dockerfiles/`, and
- two github actions workflows are stored under `.github/workflows/`:
  + `update-building-system.yml`: re-builds all scripts if any changes 
    were done in the repository (e.g. adding an R version to the `DESCRIPTION` 
    file or adding some R packages to the software bundles),
  + `publish-docker-images.yml`: actually builds and pushes the defined image
    stack.

### Updating

All scripts are automatically updated in the Github Actions Workflow 
`update-building-system.yml` (by running `execute.R`) when commited and pushed.

For adding changes (e.g. additional R packages), do:

1. *git pull* the latest changes in the remote repository,
2. *run*: 
   + `mdseasy::easy_version(element = "dev", check_renv = FALSE, check_gitlab_ci = FALSE, push = FALSE)`
3. *update* and *run* the code generating the package data 
   in `data-raw/datasets.R`,
4. *run*:
   + `devtools::document()`
   + `devtools::check()`
5. *update* `NEWS.md`
6. *run*
   + `gert::git_commit_all("YOUR COMMIT MESSAGE")`
   + `mdseasy::easy_version(check_renv = FALSE, check_gitlab_ci = FALSE)`


# Execution

The Github Actions workflow `publish-docker-images.yml` is:

- scheduled to run every Sunday,
- triggered by successful runs of the `update-building-system.yml` workflow 
  on `main` branch, 
- or can be started manually on Github.
