---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

# libraries
library(tibble)
library(dplyr)
library(purrr)
devtools::load_all(".")

# dockerhub account
account = desc::desc_get_field("Config/Dockerhub/Account")
```

# mdsrocker

<!-- badges: start -->
```{r badge, results='asis', echo=FALSE}
badge_name = "Docker Image CI"
src = glue::glue("https://github.com/{account}/mdsrocker/actions/workflows/publish-docker-images.yml/badge.svg")
href = glue::glue("https://github.com/{account}/mdsrocker/actions/workflows/publish-docker-images.yml")
glue("[![{badge_name}]({src})]({href})")
```
<!-- badges: end -->

The goal of *mdsrocker* is to provide a framework for building a stack of 
version-stable docker images based on 
[rocker/r-ver](https://hub.docker.com/r/rocker/r-ver), an *ubuntu*-based
docker image containing version-stable *base R* & a set of src build tools.

We follow the *version tag* approach of the *rocker*-project, using the image 
tag for specifying which version of R is desired (e.g. `rocker/r-ver:4.1.2`).
Omit the tag or specify `:latest` to always receive the latest versions.

## Image stack

```{r stack, echo = FALSE}

stack = rocker_dockerfiles |> 
  dplyr::select(image, description)

stack = stack |> 
  dplyr::mutate(
    image = kableExtra::cell_spec(
      image, 
      "html",
      link = glue::glue("https://hub.docker.com/r/{account}/{image}")
    )
  )

kableExtra::kable(stack, escape = FALSE)
```


## Architecture

This building system is designed as an R package. 

### Data

All relevant information is stored in *two* `data.frames` (as package data):

- `rocker_installation`: *three* different software bundles for the various
  scopes of the docker images, each containing a list of R packages and
  system libraries (not required by the R packages) to install.

```{r installation, echo = FALSE}
kableExtra::kable(rocker_installation)
```

- `rocker_dockerfiles`: *four* dockerfile specifications, each containing 
  the relevant information for generating the dockerfiles.

```{r dockerfiles, echo = FALSE}
rocker_dockerfiles |> 
  dplyr::select(-description) |> 
  kableExtra::kable()
```

### Scripts & Files

In this building system, 

- standalone shell scripts containing all the install logic are located under 
  the `scripts/` directory, 
- dockerfiles used in the Github Actions workflow to build the images are 
  located under `dockerfiles/`, and
- a github actions workflow is stored under `.github/workflows/`.

All of these files can be re-created when changes (e.g. additional R packages)
are required.

Therefore,

- update the code generating the package data in `data-raw/datasets.R`,
- re-install the package (or load using `devtools::load_all(".")`),
- run `execute.R` for calling the `create_...` functions 
  (`shellscript`, `dockerfile`, `action_workflow`) with the updated data.

# Execution

The Github Actions workflow (building and pushing the images) is scheduled to 
run every Sunday or can be started manually on Github.
